% Copyright (c) 2014,2016 Casper Ti. Vector
% Public domain.

\begin{cabstract}
	本文主要研究了临界分支过程和一类临界超过程的极限行为，以及它们与多脊柱分解理论的关系。
	特别地，本文系统地研究了临界分支过程和一类临界超过程的脊柱分解和双脊柱分解，以及它们的 Kolmogrov 型、Yaglom 型以及 Slack 型极限定理。

	本文首先给出了临界 Galton-Watson 树的脊柱分解定理和双脊柱分解定理。
	这些分解定理描述了 Galton-Watson 树的一次 size-biased 变换和二次 size-biased 变换。使用这些分解定理，本文给出了临界 Galton-Watson 过程 Yaglom 定理的一个新的直观的概率证明。
	
	接着本文建立了一类临界超过程的脊柱分解和双脊柱分解定理，并讨论了他们和这类超过程极限定理的关系。
	这两种分解分别刻画了一类具有有限二阶距的超过程的一次 size-biased 变换和二次 size-biased 变换。
	同时这两类分解可以视为泊松随机测度的一个新的分解定理的特例。
	使用这些分解，我们给出了一类具有有限二阶距的临界超过程灭绝概率和渐近行为的 Kolmogrov 型和 Yaglom 型极限定理的概率证明。
	
	然后，本文利用这些脊柱分解定理证明了超过程的特征函数满足某个非线性复值积分方程。
	该方程可以用来估计一类具有稳定分支的上临界超过程的尾概率收敛速度。
	
	最后，本文研究了一类具有空间非齐次的稳定分支的临界超过程 $\{X;\mathbf P_\mu\}$ 的 Slack 型极限定理。
	记全空间稳定系数的下确界为 $\gamma_0 > 1$。
	本文证明了，在一定条件下，$t$ 时刻的不灭绝概率 $\mathbf P_{\mu}(\|X_t\|\neq 0)$ 是以指数为 $(\gamma_0-1)^{-1}$ 正则变化的形式收敛到 $0$的；在不灭绝的条件概率下，经过适当的伸缩变换，该过程的一维分布会弱收敛到一个 Laplace 变换为
\[
	E[e^{-u\mathbf z^{(\gamma_0-1)}}]=1-(1+u^{-(\gamma_0-1)})^{-1/(\gamma_0-1)}
\]
	的严格正的随机变量 $\mathbf z^{(\gamma_0-1)}$。
\end{cabstract}

\begin{eabstract}
	This thesis focusses on the limiting theory of Galton-Watson branching processes and a class of superprocesses in the critical regime.
	Properties and relationships between their asymptotic behaviors and the multi-spine theory are considered.
	In particular, we study systematically the spine decompositions and the two-spine decompositions of critical Galton-Watson trees and a class of critical superprocesses, and their Kolmogrov type, Yaglom type and Slack type limit results. 

	We begin by proposing a two-spine decomposition of the critical Galton-Watson tree and useing that decomposition to give a new probabilistic proof of Yaglom exponential limit law.
	
	Next, we establish a spine decomposition theorem and a 2-spine decomposition theorem for some critical superprocesses. These two kinds of decompositions are unified as a decomposition theorem for size-biased Poisson random measures. We use these decompositions to give probabilistic proofs of the asymptotic behavior of the survival probability and Yaglom exponential limit law for some critical superprocesses with second moments.

	Then, using these spine decompositions, we proof that the characteristic functions of superprocesses satisfy a mild complex-valued integral equation. 
	This equation will help us to estimate the tail probability of a class of supercritical superprocesses with stable branching.

	Finally, we consider a critical superprocess $\{X;\mathbf P_\mu\}$ with general spatial motion and spatially dependent stable branching mechanism with lowest stable index $\gamma_0 > 1$. We show that, under some conditions, $\mathbf P_{\mu}(\|X_t\|\neq 0)$ converges to $0$ as $t\to \infty$ and is regularly varying with index $(\gamma_0-1)^{-1}$. Then we proof the Slack type result that for a large class of non-negative testing functions $f$, the distribution of $\{X_t(f);\mathbf P_\mu(\cdot|\|X_t\|\neq 0)\}$, after appropriate rescaling, converges weakly to a positive random variable $\mathbf z^{(\gamma_0-1)}$ with Laplace transform $E[e^{-u\mathbf z^{(\gamma_0-1)}}]=1-(1+u^{-(\gamma_0-1)})^{-1/(\gamma_0-1)}.$
\end{eabstract}

% vim:ts=4:sw=4
